taxize - taxonomic search and retrieval in R

### 2013-05-28 inst/doc/taxize_withcode.Rnw
started work on trait example

@@

It turns out that the panther has a status of endangered (EN) and the lynx has a status of least concern (LN). (ED, WHAT ELSE DO YOU WANT TO SAY HERE?)

>>>>

Trait-based approaches are a promising tool in ecology. Unlike taxonomy-based methods, traits may not be constrained to biogeographic boundaries \citep{baird_toward_2011} and have potential to disentangle the effects of multiple stressors \citep{statzner_can_2010}.

To analyse trait-composition abundance data must be matched with trait databases like \citet{usseglio-polatera_biological_2000}. However these two datatables may contain species information on different taxonomic levels and perhabs data must be aggregated to a joint taxomic level.

taxize can help in this data-cleaning step, providing a reproducible workflow. Here we illustrate this on a small fictitious example.

@@

It turns out that the panther has a status of endangered (EN) and the lynx has a status of least concern (LN).
